---
execute:
  echo: false
---

```{r, setup}
#| output: false

source("R/gen_contents.R")

```

# Contents, figures and tables {.unnumbered}

## Contents of the report

This web book version of the report is structured into 17 chapters and two
appendices.

:::{.custom-toc .report-contents}

```{r, list-sections}
#| output: asis
cat(get_content_list("sec"), sep = "\n")
```

::: {.callout-note .crf title="Cross-referencing note" icon="false"}

[Chapters 3-14](03_00_indicators.qmd) of this web book were presented as a
single chapter (Chapter 3) in the original 2019 publication. For improved
navigation and readability this part of the report has been split into separate
chapters. Footnotes have been added to charts, tables and chapters to indicate
the resulting differences in numbering between this web book and the original
PDF publication.

:::

:::

## List of figures

:::{.custom-toc .list-of-figures}

```{r, list-figures}
#| output: asis
cat(get_content_list("fig", insert_breaks = FALSE), sep = "\n")
```

:::

## List of tables

:::{.custom-toc .list-of-tables}

```{r, list-tables}
#| output: asis
cat(get_content_list("tbl"), sep = "\n")
```

:::
