---
execute:
  echo: false
---

```{r, setup}
#| output: false

source("R/gen_contents.R")

```

# Contents, figures and tables {.unnumbered}

## Contents of the report

This web book version of the report is structured into 17 chapters and two
appendices.

:::{.custom-toc .report-contents}

```{r, list-sections}
#| output: asis
cat(get_content_list("sec"), sep = "\n")
```

:::

### Changes compared to the original 2019 publication

[Chapters 3-14](03_00_indicators.qmd) of this web book were presented as a
single chapter (Chapter 3) in the original 2019 publication. For improved
navigation and readability this part of the report has been split into separate
chapters. Footnotes have been added to charts, tables and chapters to indicate
the resulting differences in numbering between this web book and the original
PDF publication.

@sec-dqa-detailed was not included in the original 2019 publication. It
has been added to this web publication of the report to provide more details
for stakeholders on the results of the data quality assessment that was used in
the 2019 modelling.

## List of figures

:::{.custom-toc .list-of-figures}

```{r, list-figures}
#| output: asis
cat(get_content_list("fig", insert_breaks = FALSE), sep = "\n")
```

:::

## List of tables

:::{.custom-toc .list-of-tables}

```{r, list-tables}
#| output: asis
cat(get_content_list("tbl"), sep = "\n")
```

:::
