---
execute:
  echo: false
---

```{r, setup}
#| output: false
library(ggplot2)
source("R/tbl_helpers.R")
source("R/gg_helpers.R")

tbl_3 <- readr::read_csv("tables/table_3.csv") |>
  dplyr::mutate(
    proxy = dplyr::if_else(proxy, "Yes", "No"),
    label = dplyr::if_else(new, paste0(label, " [new]"), label),
    wt_intheme = formattable::percent(1/wt_intheme, 1),
    wt_theme = formattable::percent(1/wt_theme, 1),
    wt_total = formattable::percent(wt_intheme * wt_theme, 1)
  )

attain_chart_df <- readr::read_csv("tables/fig-3-1-data.csv")

```

# Capabilities {#sec-method-capabilities}

<!-- This is chapter 3, section 3 in the original PDF -->

The capabilities indicator is defined as: the extent to which the workforce
has the right mix of skills. The need for a variety of certain strong skills
is vital for the successful operation of any organisation, civil services
included. The standards for good governance set out by @opm_good_2004 include
leadership as a core skill, it goes on to list necessary skills as "the ability
to scrutinise and challenge information ...including skills in financial
management and the ability to recognise when outside expert advice is needed".
@fukuyama_what_2013 acknowledges the importance of educational attainment of
civil servants: "another critical measure of capacity is the level of education
and professionalisation of government officials", along with the importance of
digital capability: "what level of technical expertise they are required to
possess".

The capabilities indicator is composed of 14 metrics from the OECD's Programme
for the International Assessment of Adult Competencies (referred to as PIAAC
from this point onwards), this is an increase of 10 metrics from the 2017 Pilot.

PIAAC is a scientific assessment of competencies in adults, modelled on the
OECD's successful Programme for International Student Assessment (PISA)
that measures the competencies of school-aged children around the world.

Data for 25 countries was collected over 2011-12, and data for nine countries
was collected over 2014-15. Of these, 31 countries have published microdata
available for analysis.

The results from PIAAC are not published in a form that allows for direct
import of the relevant data for InCiSE. Instead the data must be calculated
from the individual respondent-level microdata published by the OECD. The
microdata is analysed to produce results for those defined as currently
working in the "public administration" sector of the International Standard
Industrial Classification. This is wider than just the civil service and
includes other forms of public administration, such as sub-national and local
government, but excludes functions such as healthcare, education and transport
which may or may not be part of the public sector depending on country.

```{r}
#| label: tbl-comp-cap
#| tbl-cap: Composition of the capabilities indicator
#| column: screen-inset-right
#| classes: no-stripe .table-responsive

tbl_3 |>
  composition_table("CAP") |>
  gt::tab_footnote("Tables 3.3.A & 3.3.B in the original 2019 publication") |>
  strip_gt()

```

## Imputation of missing data {#sec-capabilities-imputation}

Of the 38 countries selected for the 2019 edition of InCiSE, 10 countries do
not have data for the capabilities metrics. As there are countries where data
is missing for all metrics the imputation of the capabilities indicator
requires a data point from outside the indicator. The 2017 edition of InCiSE
used data from the HR Management indicator on applicant skills and whether a
country was an EU member. For the 2019 edition, the applicant skills metric
from the HR management indicator is retained, but EU membership is removed.
One of the metrics within the indicator is the level of tertiary educational
attainment. There are a number of sources for estimates of tertiary educational
attainment in the general adult population of most countries. Therefore, InCiSE
also uses UNESCO data on educational attainment to impute missing data for the
capabilities indicator.

## Changes from the 2017 Pilot {#sec-capabilities-changes}

The capabilities indicator published in the2019 edition of InCiSE has had a
number of changes which improve its quality compared to the data published in
the 2017 Pilot. These include additional metrics, change in how data is
extracted, updated coding of educational attainment, and changes to imputation.
While these do not change the recency of the data, they improve the overall
quality of the information provided by the indicator. The OECD intends to
update PIAAC every decade, as annual change in the skill level of the adult
population does not change rapidly – a general principle in education research
is that educational attainment is broadly fixed after young adulthood[^caprec].
Figure 3.1, shows how the overall proportion of tertiary educational attainment
has evolved for different age groups since 1997 in four countries, the average
annual change is 0.9 percentage points.

```{r}
#| label: fig-edu-levels
#| fig-cap: Tertiary education levels of adults 25-34 and 55-64, in selected
#|   countries
#| column: body-outset-right

edu_plot <- ggplot(
  attain_chart_df,
  aes(x = year, y = value, colour = group,
      shape = group, group = group)) +
  geom_line(linewidth = 0.5) +
  geom_point(size = 1.25) +
  scale_color_manual(
    values = c(
      # canada
      "Canada 25-34 years" = "#0082c2",
      "Canada 55-64 years" = "#0082c2",
      # france
      "France 25-34 years" = "#C24113",
      "France 55-64 years" = "#C24113",
      # japan
      "Japan 25-34 years"  = "#009D94",
      "Japan 55-64 years"  = "#009D94",
      # sweden
      "Sweden 25-34 years" = "#C29913",
      "Sweden 55-64 years" = "#C29913"
    )
  ) +
  scale_shape_manual(
    values = c(
      # 25-34 years
      "Canada 25-34 years" = "circle",
      "France 25-34 years" = "circle",
      "Japan 25-34 years"  = "circle",
      "Sweden 25-34 years" = "circle",
      # 55-64 years
      "Canada 55-64 years" = "square",
      "France 55-64 years" = "square",
      "Japan 55-64 years"  = "square",
      "Sweden 55-64 years" = "square"
    )
  ) +
  scale_x_continuous(
    breaks = c(1997, 2002, 2007, 2012, 2017),
    expand = expansion(add = 1)
  ) +
  scale_y_continuous(
    limits = c(0, 62),
    breaks = seq(0, 60, 10),
    labels =  scales::percent_format(accuracy = 0.1, scale = 1),
    expand = expansion(add = 1)
  ) +
  facet_grid(cols = vars(country)) +
  guides(
    colour = guide_legend(title = NULL, nrow = 2, ncol = 4),
    shape = guide_legend(title = NULL, nrow = 2, ncol = 4)
  ) +
  theme_minimal() +
  theme(
    text = element_text(colour = "#666666", family = "Inter", size = 14),
    legend.position = "bottom",
    axis.title = element_blank(),
    axis.text = element_text(colour = "#666666"),
    axis.text.x = element_text(angle = 90),
    strip.text = element_text(hjust = 0, colour = "#666666", face = "bold",
                              size = 14),
    panel.background = element_rect(fill = "#edf6fb", colour = NA),
    panel.grid.major = element_line(colour = "#ffffff"),
    panel.grid.minor = element_blank(),
    plot.background = element_rect(fill = "#fafdfe", colour = NA)
  )

render_svg(edu_plot, width = 700, height = 600,
           alt_text = paste(
             "Four line graphs showing the proportion of adults with teritary",
             "eduation (e.g. a university Bachelor's degree) between 1997 and",
             "2017 for those aged 25 to 34 years old and those aged 55-64",
             "years old in each of Canada, France, Japan and Sweden.",
             "The graph shows a broadly linear increase in attainment levels",
             "for each age group and a consistent gap between age-groups."
             ),
           source_note = paste(
             "Source: OECD (2023), Population with tertiary education.",
             "doi: 10.1787/0b8f90e9-en (Accessed on 28 November 2023).",
             "<br>This chart varies slightly from that included in the original",
             "published PDF report due to changes in data availability.",
             "The original chart included data for the age groups 25-34, 35-44",
             "and 45-54, however the source data at the time of this",
             "reproduction (November, 2023) provides data for those aged",
             "25-35 and 55-64.",
             "<br>This chart was Figure 3.1 in the original 2019 publication"
             )
           )

```

### Additional metrics
In examining the PIAAC dataset, a number of additional metrics that complement
the metrics used in the pilot provide a richer picture of capabilities in the
public administration workforce.

The pilot metrics gave a broad overview of employee capability, looking at
overall levels of core skills (literacy, numeracy and problem solving) and
tertiary educational attainment. The additional metrics complement this by
providing for measurement of the use of core skills at work (ICT, numeracy,
reading and writing). They also cover more complex skills, including
influencing others, planning, and task management. Finally, they also include
metrics relating to learning and development --- whether individuals learn at
work, their overall attitude to learning, and whether they have participated
in learning for work-related purposes (either formallyor informally). Together
these metrics provide a more detailed picture of the skills and capabilities
of the workforce.

### Using the public administration industrial sector {.unnumbered}
The pilot edition of InCiSE used data for all adults currently employed by a
public sector organisation. Further investigations of the raw data in PIAAC
indicated that there was a sufficient sample size in most countries (n>100) to
generate an estimate for the "public administration" industry
sector[^capsmpl] and worked for a public sector organisation.

There is a considerable difference between countries with regard to whether
someone is a public sector worker. This is in part due to the political choices
about what is or isn't delivered by the public sector. For example, in the
United Kingdom the vast majority of healthcare workers will be public sector
employees, while in the United States the vast majority of healthcare workers
will be private sector employees. In contrast, this difference is likely to be
much reduced for the "public administration" industry sector, as it will not
include sectors such as healthcare, education or competitive market economic
sectors. Therefore, while the sample size for the "public administration"
subset will be lower, it is likely to be a more appropriate comparator group
across countries than using the large "public sector" basis.

Further details on the structure of the activities included in the
"public administration" industrial sector can be found in the UN's registry of
Statistical Classifications [@unsd_statistical_2018].

### Updated coding of tertiary education

In reviewing the way that results are extracted from PIAAC's raw data files,
an improvement was identified in the way tertiary education is coded. The
pilot edition of InCiSE used data from a variable included for legacy
comparisons with previous international assessments of adult competencies
based on type of institution attended. InCiSE 2019 uses a more accurate method
based on the highest level of qualification achieved.

### Updating the approach to imputation

In the pilot edition of InCiSE, missing data issues were handled by examining
the relationship of the metrics from PIAAC with metrics from the other
indicators in InCiSE (as PIAAC is the only data source for the capabilities
indicator). The most suitable predictors observed in the dataset were the
applicant skills metric from the HR management indicator and whether a country
was an EU member. As described above, the imputation for the 2019 edition has
changed the methodology to remove the EU membership criteria and include the
tertiary education level of the general population in the external imputation
data. This provides a closer link to the indicator's theoretical construct.

::: {.callout-note .crf title="Cross-referencing note" icon="false"}

This chapter was presented as section 3.3 in the original 2019 publication.

:::


[^caprec]: @lutz_reconstruction_2007 and @goujon_harmonized_2016 utilise this
principle to develop "back-projections" of educational attainment, and hold a
general assumption that 'transition' to different levels of education tend to
be limited after the age of 34.

[^capsmpl]: Sample sizes for the public administration industry sector (limited
to declared public sector workers) range from 83 to 1,562. The minimum and
maximum are both noticeable outliers: ignoring these, the sample sizes range
from 144-446. The only country with a sample less than 100 (Russian Federation)
had similar standard errors to those of other countries and therefore was
retained in the data extracted from PIAAC.

