---
execute:
  echo: false
---

```{r, setup}
#| output: false
source("R/tbl_helpers.R")

tbl_3 <- readr::read_csv("tables/table_3.csv") |>
  dplyr::mutate(
    proxy = dplyr::if_else(proxy, "Yes", "No"),
    label = dplyr::if_else(new, paste0(label, " [new]"), label),
    wt_intheme = formattable::percent(1/wt_intheme, 1),
    wt_theme = formattable::percent(1/wt_theme, 1),
    wt_total = formattable::percent(wt_intheme * wt_theme, 1)
  )

```

# Openness {#sec-method-openness}

<!-- This is chapter 3, section 2 in the original PDF -->

The openness indicator is defined as: the regular practice and degree of
consultation with citizens to help guide the decisions we make and extent of
transparency in our decision-making. It is included in the index because the
need for transparency within a civil service is imperative for the public to
trust and feel empowered to hold the government accountable for their actions,
whilst at the same time reducing corruption. The @world_bank_world_2017 notes 
that "transparency initiatives [are] an important first step toward increasing
accountability". The UN also outlines the need for transparency and
accountability in governance: "[this] implies a proactive effort to make
information accessible to citizens" and it is "one indicator of a government
that is citizen-focused and service-oriented" [@united_nations_transparency_1999].
@graham_principles_2003 also refer to the United Nations Development Program's
five principles of good governance, in which transparency is identified as a key
characteristic.

This indicator is comprised of 10 metrics, an increase of one from the 2017
Pilot edition of InCiSE. The data sources for the openness indicator are:

* The open government domain of the World Justice Project's Rule of Law Index
  (RLI) [2017].
* The United Nations' E-Participation Index(UN) [2018].
* Bertelsmann Stiftung's Sustainable Governance Indicators (SGI) [2018].
* The World Wide Web Foundation's Open Data Barometer (ODB) [2016].
* Open Knowledge International's Global Open Data Index (OKI) [2016].
* The OECD's Open, Useful, Reusable (OUR) Government Data Index (OECD) [2016].

```{r}
#| label: tbl-comp-opn
#| tbl-cap: Composition of the openness indicator
#| column: screen-inset-right
#| classes: no-stripe .table-responsive

tbl_3 |>
  composition_table("OPN") |>
  gt::tab_footnote("Tables 3.2.A & 3.2.B in the original 2019 publication") |>
  strip_gt()

```

## Imputation of missing data {#sec-openness-imputation}

None of the 38 countries selected for the 2019 edition of InCiSE have
completely missing data for the openness metrics. As a result the imputation
of missing data for the openness metrics is based solely on the data within
the indicator.

## Changes from the 2017 Pilot {#sec-openness-changes}

Compared to the 2017 Pilot, an additional metric from the Bertelsmann
Sustainable Governance Indicators on access to information has been identified
and added to the indicator.

::: {.callout-note .crf title="Cross-referencing note" icon="false"}

This chapter was presented as section 3.2 in the original 2019 publication.

:::
