---
execute:
  echo: false
---

```{r, setup}
#| output: false
source("R/tbl_helpers.R")

tbl_3 <- readr::read_csv("tables/table_3.csv") |>
  dplyr::mutate(
    proxy = dplyr::if_else(proxy, "Yes", "No"),
    label = dplyr::if_else(new, paste0(label, " [new]"), label),
    wt_intheme = formattable::percent(1/wt_intheme, 1),
    wt_theme = formattable::percent(1/wt_theme, 1),
    wt_total = formattable::percent(wt_intheme * wt_theme, 1)
  )

```

# Regulation {#sec-method-regulation}

<!-- This is chapter 3, section 7 in the original PDF -->

The regulation indicator is defined as: the extent and quality of regulatory
impact assessments and the degree of stakeholder engagement involved in them. The appropriate appraisal and evaluation of regulatory changes accompanied by
sufficient stakeholder engagement is crucial to ensuring that any
introductions are fully considered and fair, involving various stakeholders.
This scrutiny is endorsed by many; the @oecd_recommendation_2012 for instance,
"recognis[es] that regulations are one of the key levers by which governments
act to promote economic prosperity, enhance welfare and pursue the public
interest", and that "well designed regulations can generate significant social
and economic benefits which out weigh the costs of regulation, and contribute
to social well-being". The @international_monetary_fund_consultation_2016
acknowledges the importance of regulatory frameworks to successful governance:
"From the perspective of the IMF, countries with good governance have strong
legal and regulatory frameworks in place". Additionally, in promoting best
practice, "[the] Regulatory Impact Analysis (RIA) is a multiple stakeholder
assessment of the economic, environmental and social impact of regulations.
The OECD and European Union have strongly promoted this evidence-based
approach towards legislation" [@boviard_public_2003].

The regulation indicator is comprised of nine metrics, an increase of three
from the 2017 Pilot. It uses the following sources:

* The OECD's Indicators of Regulatory Policy and Governance (OECD) [2017].
* The Bertelsmann Foundation's Sustainable Governance Indicators (SGI) [2018].

```{r}
#| label: tbl-comp-reg
#| tbl-cap: Composition of the regulation indicator
#| column: screen-inset-right
#| classes: no-stripe .table-responsive

tbl_3 |>
  composition_table("REG") |>
  gt::tab_footnote("Tables 3.7.A & 3.7.B in the original 2019 publication") |>
  strip_gt()

```

## Imputation of missing data {#sec-regulation-imputation}

None of the 38 countries selected for the 2019 edition of InCiSE have
completely missing data for the regulation metrics. As a result the imputation
of missing data for the regulation metrics is based solely on the data within
the indicator.

## Changes from the 2017 Pilot {#sec-regulation-changes}

The regulation indicator has had three additional metrics added from the
Bertelsmann Foundation's Sustainable Governance Indicators on the use and
quality of regulatory impact assessments (RIA), and whether RIAs include
sustainability checks.

::: {.callout-note .crf title="Cross-referencing note" icon="false"}

This chapter was presented as section 3.7 in the original 2019 publication.

:::
