---
execute:
  echo: false
---

```{r, setup}
#| output: false
library(ggplot2)
source("R/tbl_helpers.R")
source("R/gg_helpers.R")

tbl_3 <- readr::read_csv("tables/table_3.csv") |>
  dplyr::mutate(
    proxy = dplyr::if_else(proxy, "Yes", "No"),
    label = dplyr::if_else(new, paste0(label, " [new]"), label),
    wt_intheme = formattable::percent(1/wt_intheme, 1),
    wt_theme = formattable::percent(1/wt_theme, 1),
    wt_total = formattable::percent(wt_intheme * wt_theme, 1)
  )

```

# Policy making {#sec-method-policy}

<!-- This is chapter 3, section 5 in the original PDF -->

The policy making indicator is defined as: the quality of the policy making
process, including how policy is developed and coordinated across government
and how policy is monitored during implementation. Policy making remains a
central role of a civil service and the quality of evidence and appraisal are
central to the success of policy. @kaufman_governance_1999 outline three
functions of good governance, including "the capacity of government to
effectively formulate and implement sound policies". Policymakers need to
"receive rigorous analyses of comprehensive background information and
evidence, and of the options for actions" according to @opm_good_2004. This
paper also advises that "good quality information and clear, objective advice
can significantly reduce the risk of taking decisions that fail to achieve
their objectives or have serious unintended consequences".

The indicator is comprised of eight metrics, and the structure is unchanged
from the 2017 Pilot edition of InCiSE. The policy making indicator uses a
single source, the Bertelsmann Stiftung's Sustainable Government Indicators
(SGI), an expert assessment of the performance of government in EU and OECD
countries. The data for the 2019 edition of InCiSE use the 2018 edition of the
SGIs.

```{r}
#| label: tbl-comp-pol
#| tbl-cap: Composition of the policy making indicator
#| column: screen-inset-right
#| classes: no-stripe .table-responsive

tbl_3 |>
  composition_table("POL") |>
  gt::tab_footnote("Tables 3.5.A & 3.5.B in the original 2019 publication") |>
  strip_gt()

```

## Imputation of missing data {#sec-policy-imputation}

All 38 countries selected for the 2019 edition of InCiSE have data for all the
metrics in the policy making indicator. Therefore, no approach to imputation
is needed.

## Changes from the 2017 Pilot {#sec-policy-changes}

The policy making indicator is unchanged from the 2017 Pilot edition.

::: {.callout-note .crf title="Cross-referencing note" icon="false"}

This chapter was presented as section 3.5 in the original 2019 publication.

:::
