---
execute:
  echo: false
---

```{r, setup}
#| output: false
source("R/tbl_helpers.R")

tbl_3 <- readr::read_csv("tables/table_3.csv") |>
  dplyr::mutate(
    proxy = dplyr::if_else(proxy, "Yes", "No"),
    label = dplyr::if_else(new, paste0(label, " [new]"), label),
    wt_intheme = formattable::percent(1/wt_intheme, 1),
    wt_theme = formattable::percent(1/wt_theme, 1),
    wt_total = formattable::percent(wt_intheme * wt_theme, 1)
  )

```

# Inclusiveness {#sec-method-inclusiveness}

<!-- This is chapter 3, section 4 in the original PDF -->

The inclusiveness indicator is defined as: the extent to which the civil
service is representative of the citizens it serves. A model civil service
should be representative of the public it stands to serve, and therefore
institutions must be inclusive in nature. In their Post-2015 Millennium
Development Goal reflections, the @oecd_building_nodate outlines the greater
success felt by inclusive public bodies: "Inclusive governments and an active
civil society put forward more responsive, equitable policies" and that these
"build trust in government and help create... public services that are better
suited to diverse needs". The guiding principles to the international civil
service, set out by the International Civil Service Commission, support the
claim that civil servants must "respect the dignity, worth and equality of all
people" and have: "a willingness to work without bias with persons of all
nationalities, religions and cultures"
[-@international_civil_service_commission_standards_2002].

The @oecd_government_2015 states that "a more representative public
administration can better access previously overlooked knowledge, networks and
perspectives for improved policy development and implementation". The same
report also points out that the opinion on the groups in need of representation
in public administration has widened "and now includes a range of dimensions
such as women; racial, ethnic, and religious
minorities; the poor; the elderly; the disabled; and other minority groups
such as indigenous populations". A paper by @opm_good_2004 highlights the
potential benefits of this view: "Public trust and confidence in governance will
increase if governance  ... [is] done by a diverse group of people who reflect
the community".

The inclusiveness indicator is comprised of five metrics, and is unchanged in
structure from the 2017 Pilot. It uses the following source data:

* OECD data on the central government share of women in the central
  government and in top management positions [2016], as processed and
  published in their Government at a Glance 2017 report.
* The University of Gothenburg's Quality of Government Expert Survey
  (QoG) [2015].
* Figures on women's representation in the government workforce are compared
  to data from the International Labour Organisation on the composition to
  calculate the difference between government and the workforce as a whole
  (ILO) [2015].

```{r}
#| label: tbl-comp-inc
#| tbl-cap: Composition of the inclusiveness indicator
#| column: screen-inset-right
#| classes: no-stripe .table-responsive

tbl_3 |>
  composition_table("INC") |>
  gt::tab_footnote("Tables 3.4.A & 3.4.B in the original 2019 publication") |>
  strip_gt()

```

## Imputation of missing data {#sec-inclusiveness-imputation}

None of the 38 countries selected for the 2019 edition of InCiSE have
completely missing data for the inclusiveness metrics. As a result the
imputation of missing data for the inclusiveness metrics is based solely on
the data within the indicator.

## Changes from the 2017 Pilot {#sec-inclusiveness-changes}

There are no changes in the structure of the inclusivness indicator from the
2017 Pilot.

::: {.callout-note .crf title="Cross-referencing note" icon="false"}

This chapter was presented as section 3.4 in the original 2019 publication.

:::
