---
execute:
  echo: false
---

```{r, setup}
#| output: false
library(ggplot2)
source("R/tbl_helpers.R")
source("R/gg_helpers.R")

tbl_3 <- readr::read_csv("tables/table_3.csv") |>
  dplyr::mutate(
    proxy = dplyr::if_else(proxy, "Yes", "No"),
    label = dplyr::if_else(new, paste0(label, " [new]"), label),
    wt_intheme = formattable::percent(1/wt_intheme, 1),
    wt_theme = formattable::percent(1/wt_theme, 1),
    wt_total = formattable::percent(wt_intheme * wt_theme, 1)
  )

tbl_pemp_2017 <- read_md_tbl("tables/table_3-1-C.txt")
tbl_pemp_2019 <- read_md_tbl("tables/table_3-1-D.txt")
tbl_egbr_nat <- read_md_tbl("tables/table_3-12-C.txt")

attain_chart_df <- readr::read_csv("tables/fig-3-1-data.csv")

tbl_egbr_nat <- tbl_egbr_nat |>
  dplyr::mutate(
    median_national = convert_percent(median_national)
  )

```

# Procurement {#sec-method-procurement}

<!-- This is chapter 3, section 9 in the original PDF -->

The procurement indicator is defined as: the extent to which the government's
procurement processes are efficient, competitive, fair and pursues value for
money. According to the @world_trade_organisation_government_2015 "government 
procurement accounts for an average of 15 percent of more of a country's GDP".
As procurement makes up such a large proportion of countries' GDP, it must be
managed appropriately. Effective procurement management can streamline
contracts and reduce outgoings, contributing to improved efficiencies in civil
services. On public procurement, the @world_bank_benchmarking_2016 states it
"is a key variable in determining development outcomes and, when carried out in
an efficient and transparent manner, it can play a strategic role in delivering
more effective public services. It can also act as a powerful tool for
development with profoundly positive repercussions for both good governance
and more rapid and inclusive growth".

The procurement indicator is comprised of six metrics. This indicator is new
for the 2019 edition of the index, and was not included in the 2017 Pilot
edition. The sources for the procurement indicator are:

* The OECD's Public Procurement Survey [2016].
* Opentender (OT) analysis of European public procurement data by Digiwhist
  (a collaboration of the University of Cambridge, Open Knowledge Foundation
  Germany, Government Transparency Institute, Hertie School of Governance,
  Datlab and Transcrime) [2016].

```{r}
#| label: tbl-comp-pro
#| tbl-cap: Composition of the procurement indicator
#| column: screen-inset-right
#| classes: no-stripe .table-responsive

tbl_3 |>
  composition_table("PRO") |>
  gt::tab_footnote("Tables 3.9.A & 3.9.B in the original 2019 publication") |>
  strip_gt()

```

## Imputation of missing data {#sec-procurement-imputation}

Two of the 38 countries selected for the 2019 edition of InCiSE have
completely missing data for the procurement indicator.

The procurement indicator is a new indicator for the 2019 edition, and there
are no easily identifiable external predictors (e.g. tertiary education for
Capabilities or the UN's E-Government survey for Digital Services), instead
the correlations between the procurement metrics and the other metrics in the
InCiSE model have been analysed to identify potential predictors. This
analysis has selected three metrics: the use of data in HR administration from
the HR management indicator; the publicised laws metric from the openness
indicator; and, the collection cost metric from the tax administration
indicator.

## Changes from the 2017 Pilot {#sec-procurement-changes}

The procurement indicator is a new indicator and was not covered by the 2017
Pilot edition of the InCiSE Index.

::: {.callout-note .crf title="Cross-referencing note" icon="false"}

This chapter was presented as section 3.9 in the original 2019 publication.

:::
