---
execute:
  echo: false
---

```{r, setup}
#| output: false
source("R/tbl_helpers.R")

tbl_3 <- readr::read_csv("tables/table_3.csv") |>
  dplyr::mutate(
    proxy = dplyr::if_else(proxy, "Yes", "No"),
    label = dplyr::if_else(new, paste0(label, " [new]"), label),
    wt_intheme = formattable::percent(1/wt_intheme, 1),
    wt_theme = formattable::percent(1/wt_theme, 1),
    wt_total = formattable::percent(wt_intheme * wt_theme, 1)
  )

tbl_pemp_2017 <- read_md_tbl("tables/table_3-1-C.txt")
tbl_pemp_2019 <- read_md_tbl("tables/table_3-1-D.txt")

```

# Integrity {#sec-method-integrity}

<!-- This is chapter 3, section 1 in the original 2019 publication -->

The integrity indicator is defined as: the extent to which civil servants
behave with integrity, make decisions impartially and fairly, and strive to
serve both citizens and ministers, and is one of the core values associated
with a civil service. The International Civil Service Commission 
[-@international_civil_service_commission_standards_2002] highlights
the importance of integrity to the work of the United Nations (UN) common
systems staff: "The concept of integrity ... embraces all aspects of behaviour
of an international civil servant ... including  ... honesty, truthfulness,
impartiality and incorruptibility. These qualities are as basic as those of
competence and efficiency". Numerous studies aiming to establish good
governance have utilised similar metrics in their analyses, for instance
@muriithi_quantifying_2015. The inclusion of integrity in the InCiSE is
therefore deemed necessary and crucial for the assessment of an effective
civil service.

The indicator for integrity is comprised of 17 metrics – an increase of one
from the 2017 Pilot edition. A change has also been made in the metric on
post-employment cooling-off in the way it has been coded from the source data.

The following sources are used:

* Transparency International's Global Corruption Barometer (GCB) [2017].
* The World Economic Forum's Global Competitiveness Report Executive
  Opinion Survey (WEF) [2016-2017].
* The University of Gothenburg's Quality of Government Expert Survey
  (QoG) [2015].
* The OECD's Survey on Managing Conflict of Interest in the Executive Branch
  and Whistleblower Protection [2014] and Survey on Lobbying Rules and
  Guidelines [2013] as processed and published in their Government at a Glance
  2015 report.
* The Bertelsmann Foundation's Sustainable Governance Indicators (SGI) [2018].

```{r}
#| label: tbl-comp-int
#| tbl-cap: Composition of the integrity indicator
#| column: screen-inset-right
#| classes: no-stripe .table-responsive

tbl_3 |>
  composition_table("INT") |>
  gt::tab_footnote("Tables 3.1.A & 3.1.B in the original 2019 publication") |>
  strip_gt()

```

## Imputation of missing data {#sec-integrity-imputation}

None of the 38 countries selected for the 2019 edition of InCiSE have
completely missing data for the integrity metrics. As a result the imputation
of missing data for the integrity metrics is based solely on the data within
the indicator.

## Changes from the 2017 pilot {#sec-integrity-changes}

There is one proposed change to the structure of the metrics used in the
calculation of the integrity indicator: the inclusion of a measure from the
Bertelsmann Foundation's Sustainable Governance Indicators on corruption
prevention.

A further change from the 2017 pilot methodology has been implemented in the
processing of the OECD's data on post-employment cooling-off periods. The
model now simply codes whether post-employment cooling-off periods and now
ignores whether compensation is paid during this period.

The OECD source data provides information on whether post-employment
cooling-off periods exist for both senior civil servant sand other
civil servants, and also includes information on whether a compensation period
is paid during that period.

These data are combined by the InCiSE model into a single scale, outlined
below. In the 2017 Pilot, this scale creates the normative conditions that a
post-employment cooling-off period with compensation for both groups of civil
servants is "best" and no cooling-off period is "worst", @tbl-pemp-2017.

```{r}
#| label: tbl-pemp-2017
#| tbl-cap: Coding of post-employment cooling-off in the 2017 Pilot edition
#|   of InCiSE
#| classes: no-stripe .table-responsive

tbl_pemp_2017 |>
  gt::gt(
    groupname_col = "pemp_2017",
    row_group_as_column = TRUE
  ) |>
  gt::tab_stubhead(label = "InCiSE 2017 post-employment scale value") |>
  gt::cols_label(
    scs_cool = "Cooling-off period?",
    scs_comp = "With compensation?",
    ocs_cool = "Cooling-off period?",
    ocs_comp = "With compensation?"
  ) |>
  gt::tab_spanner(
    label = "Senior civil servants", columns = c(scs_cool, scs_comp)
  ) |>
  gt::tab_spanner(
    label = "Other civil servants", columns = c(ocs_cool, ocs_comp)
  ) |>
  gt::tab_footnote("Table 3.1.C in the original 2019 publication") |>
  strip_gt()

```

Further examination of the data, as reported by the OECD, showed that only a
limited number of officials in only a small number of countries received paid
compensation during a cooling off period and that there was noticeable
variation in how this was decided by country. This limited usage of
post-employment compensation and high variability in its nature suggests that
it may not be appropriate to code in the provision of post-employment
compensation as normative "best" practice in the calculation of the integrity
indicator.

> *"During the cooling off period, only some categories of public officials in
  Austria, Israel, Norway, Portugal and Spain receive compensation. For
  instance, in Spain, public officials receive 80% of their basic salaries
  as compensation and in Norway, compensation is awarded only for prohibitions
  on taking up a specific appointment, the level of which is equivalent to the
  salary received at the time of the public official left public office"*
  [@oecd_government_2015 p. 116]

Therefore, for the 2019 edition, InCiSE has adopted a new scale that measures
only the existence of post-employment cooling-off periods for senior civil
servants and other civil servants, ignoring the use/existence of compensation,
@tbl-pemp-2019. The highest score will be awarded for those countries that have
a cooling-off period for both groups of civil servants, the lowest score for
those that do not have a cooling-off period for either group, while an
intermediate score will be given to those countries that have a cooling-off
period for one group but not the other – with cooling-off periods for senior
civil servants preferred to those for non-senior civil servants.

```{r}
#| label: tbl-pemp-2019
#| tbl-cap: Coding of post-employment cooling-off in the 2019 edition
#|   of InCiSE
#| classes: .table-responsive

tbl_pemp_2019 |>
  gt::gt(
    groupname_col = "pemp_2019",
    row_group_as_column = TRUE
  ) |>
  gt::tab_stubhead(label = "InCiSE 2019 post-employment scale value") |>
  gt::cols_label(
    scs_cool = "Senior civil servants",
    ocs_cool = "Other civil servants"
  ) |>
  gt::tab_spanner(
    label = "Does a post-employment cooling-off period exist for...?",
    columns = c(scs_cool, ocs_cool)
  ) |>
  gt::tab_footnote("Table 3.1.D in the original 2019 publication") |>
  strip_gt()

```

::: {.callout-note .crf title="Cross-referencing note" icon="false"}

This chapter was presented as section 3.1 in the original 2019 publication.

:::
