---
execute:
  echo: false
---

```{r, setup}
#| output: false
library(ggplot2)
source("R/tbl_helpers.R")
source("R/gg_helpers.R")

tbl_3 <- readr::read_csv("tables/table_3.csv") |>
  dplyr::mutate(
    proxy = dplyr::if_else(proxy, "Yes", "No"),
    label = dplyr::if_else(new, paste0(label, " [new]"), label),
    wt_intheme = formattable::percent(1/wt_intheme, 1),
    wt_theme = formattable::percent(1/wt_theme, 1),
    wt_total = formattable::percent(wt_intheme * wt_theme, 1)
  )

```

# Fiscal and financial management {#sec-method-fiscal}

<!-- This is chapter 3, section 6 in the original PDF -->

The fiscal and financial management indicator is defined as: The quality of
the budgeting process and the extent to which spending decisions are informed
through economic appraisal and evaluation. It is an important measure of every
system of public administration. The Indicator of the Strength of Public
Management Systems (ISPMS) from the @world_bank_indicators_2012 state "Public
sector management arrangements must also encourage fiscal and institutional sustainability as less tangible but equally critical outcomes" and "Reforms of
budgetary and financial management systems ... are often crucial for development outcomes". @holt_fukuyama_2014 also consider that "public administration
practitioners break down the functioning of the central agencies into five
management systems", including fiscal and financial management which is made
up of: "planning and budgeting; financial management; and accounting, fiscal
reporting and audit". The OECD's recommendation paper on budgetary governance
[-@oecd_recommendation_2015] also sets out ten principles for good budgetary
governance which include "ensur[ing] that performance, evaluation, and value
for money are integral to the budget process ... [and] ...manag[ing] budgets
within clear, credible and predictable limits for fiscal policy".

The fiscal and financial management indicator is made up of six metrics, an
increase of three from the 2017 Pilot. The sources for the indicator are:

* The OECD's 'medium-term budgeting index' [2012] and 'performance budgeting
  index' [2016].
* The World Economic Forum's Global Competitiveness Index (WEF) [2016 2017].
* World Bank Financial Management Information Systems & Open Budget Data
  (WB) [2017].
* International Budget Partnership' s Open Budget Survey (IBP) [2017].

```{r}
#| label: tbl-comp-ffm
#| tbl-cap: Composition of the fiscal and financial management indicator
#| column: screen-inset-right
#| classes: no-stripe .table-responsive

tbl_3 |>
  composition_table("FFM") |>
  gt::tab_footnote("Tables 3.6.A & 3.6.B in the original 2019 publication") |>
  strip_gt()

```

## Imputation of missing data {#sec-fiscal-imputation}

None of the 38 countries selected for the 2019 edition of InCiSE have
completely missing data for the fiscal and financial management metrics. As a
result the imputation of missing data for the fiscal and financial management
metrics is based solely on the data within the indicator.

## Changes from the 2017 Pilot {#sec-fiscal-changes}

The fiscal and financial management indicator has seen the introduction of
three new data points to increase the scope and robustness of the indicator.
These include a metric on the publication of medium-term budgeting data from
the World Bank into the theme of the same name and two new metrics under the
economic appraisal and evaluation theme: two data points measuring the extent
of external scrutiny or audit and two data points measuring the extent of
transparency based on the publication of budgetary reports.

::: {.callout-note .crf title="Cross-referencing note" icon="false"}

This chapter was presented as section 3.6 in the original 2019 publication.

:::
