---
execute:
  echo: false
---

```{r, setup}
#| output: false
source("R/tbl_helpers.R")

tbl_3 <- readr::read_csv("tables/table_3.csv") |>
  dplyr::mutate(
    proxy = dplyr::if_else(proxy, "Yes", "No"),
    label = dplyr::if_else(new, paste0(label, " [new]"), label),
    wt_intheme = formattable::percent(1/wt_intheme, 1),
    wt_theme = formattable::percent(1/wt_theme, 1),
    wt_total = formattable::percent(wt_intheme * wt_theme, 1)
  )

```

# Crisis and risk management {#sec-method-crisis}

<!-- This is chapter 3, section 8 in the original PDF -->

The crisis and risk management indicator is defined as: the effectiveness with
which the government engages the whole of society to better assess, prevent,
respond to and recover from the effects of extreme events. The OECD Strategic
Crisis Management report highlights crisis management as central to
government's role and a "fundamental element of good governance"
[@baubion_oecd_2013]. Studies have shown that credibility and trust in
governments to deal with crises is vital both to reassure and encourage support
from the private sector and general public, as outlined by
@christensen_crisis_2011.

The crisis and risk management indicator is made up of 13 metrics. This is an
increase of four from the 2017 Pilot, however it has been restructured to
allow for the inclusion of a new data source, with eight metrics continuing
from the 2017 Pilot and five new metrics. The data for the indicator comes
from:

* The United Nation's Hyogo Framework for Action monitoring reports [2015].
* The OECD's Survey on the Governance of Critical Risk [2016].

Both the Hyogo Framework monitoring reports and the OECD survey are largely
composed of binary yes/no questions. The InCiSE model has undertaken its own analysis and aggregation of these measures to produce metrics for the crisis and risk management indicator. These are listed in detail in @sec-composite-crm.

```{r}
#| label: tbl-comp-crm
#| tbl-cap: Composition of the crisis and risk management indicator
#| column: screen-inset-right
#| classes: no-stripe .table-responsive

tbl_3 |>
  composition_table("CRM") |>
  gt::tab_footnote("Tables 3.8.A & 3.8.B in the original 2019 publication") |>
  strip_gt()

```

## Imputation of missing data {#sec-crisis-imputation}

One of the 38 countries selected for the 2019 edition of InCiSE has completely
missing data for all crisis and risk management metrics. This is an
improvement on the 2017 Pilot of InCiSE where eight countries had completely
missing data. The 2017 Pilot used median imputation to handle missing data for
the crisis and risk management indicator (i.e. replacement of missing values
with the median value of the included countries). As a result of the decision
to move to fully predictive imputation for the 2019 edition, external
predictors needed to be found. There are no easily identifiable external
predictors (e.g. tertiary education for capabilities or the UN's E-Government
survey for digital services), instead the correlations between the crisis and
risk management metrics and other metrics in the InCiSE model have been
analysed to identify potential predictors. This analysis has selected three
metrics: the task discretion metric from the capabilities indicator; the use
of data in HR administration from the HR management indicator; and, the Open
Data Index from the openness indicator.

## Changes from the 2017 Pilot {#sec-crisis-changes}

The 2017 Pilot used data solely from the national monitoring and progress
reports of the UN Hyogo Framework for Action. The Hyogo Framework for Action
ended in 2015 and has been replaced by the Sendai Framework, however
monitoring and reporting of this framework has only just begun. Furthermore,
these frameworks focus on natural disaster risk rather than the full range of
risks and civil contingencies issues that countries have to manage at a
central government level. Since the publication of the pilot a further dataset
has become available, the OECD's Survey of the Governance of Critical Risks.
This dataset provides data on this wider array of risks that governments,
especially OECD members, tend to manage.

::: {.callout-note .crf title="Cross-referencing note" icon="false"}

This chapter was presented as section 3.8 in the original 2019 publication.

:::
