---
execute:
  echo: false
---

```{r, setup}
#| output: false
library(ggplot2)
source("R/tbl_helpers.R")
source("R/gg_helpers.R")

tbl_3 <- readr::read_csv("tables/table_3.csv") |>
  dplyr::mutate(
    proxy = dplyr::if_else(proxy, "Yes", "No"),
    label = dplyr::if_else(new, paste0(label, " [new]"), label),
    wt_intheme = formattable::percent(1/wt_intheme, 1),
    wt_theme = formattable::percent(1/wt_theme, 1),
    wt_total = formattable::percent(wt_intheme * wt_theme, 1)
  )

tbl_egbr_nat <- read_md_tbl("tables/table_3-12-C.txt")

tbl_egbr_nat <- tbl_egbr_nat |>
  dplyr::mutate(
    median_national = convert_percent(median_national)
  )

```

# Digital services {#sec-method-digital}

<!-- This is chapter 3, section 12 in the original PDF -->

The digital services indicator in InCiSE is defined as the user-centricity
and cross-border mobility of digitally-provided public services and the
availability of 'key enablers'. A changing world and digital environment
provide the impetus for a civil service to ensure modernity and remain
user-centric for the public. In doing so, efficiencies should be achieved to
enable cost savings in processes while also allowing for further
accessibility of services. The OECD has supported this view of potential
benefits: "ICT is increasingly used to support broader public sector
development objectives ... by changing service delivery approaches by creating
personalised, high quality services to users, thereby increasing user
satisfaction and effective service delivery; facilitating major work
organisation and management changes creating back-office coherence and
efficiency gains; increasing transparency of government activities, and
increasing citizen engagement" [@lonti_towards_2008].

The source data for the digital services indicator is the European Commission's
eGovernment Benchmark Report (eGBR) 2017 and 2018 reports, which provide data
for 2016 and 2017 respectively. This is the same source that was used in the
2017 Pilot, however significant changes have been made to the way in which the
data is extracted and imported. The 2019 edition of the digital services
indicator is composed of 13 metrics, compared to four in the 2017 Pilot.

```{r}
#| label: tbl-comp-dig
#| tbl-cap: Composition of the digital services indicator
#| column: screen-inset-right
#| classes: no-stripe .table-responsive

tbl_3 |>
  composition_table("DIG") |>
  gt::tab_footnote("Tables 3.12.A & 3.12.B in the original 2019 publication") |>
  strip_gt()

```

## Imputation of missing data {#sec-digital-imputation}

Nine of the 38 countries selected for the 2019 edition of InCiSE have
completely missing data for the digital services indicator. The 2017 Pilot of
the InCiSE Index set out the use of Online Services Index from the UN's
biennial E-Government Survey as the external predictor for imputation. This
approach is maintained for the 2019 edition of the InCiSE Index.

## Changes from the 2017 Pilot {#sec-digital-changes}

The data source used for the digital services indicator in the 2019 edition of
InCiSE is the same as that used for the 2017 Pilot – the European Commission's
eGovernment Benchmark Report (eGBR). However, further investigation of the data
and methodology of the report has led to a change in the metrics used by
InCiSE. While the 2017 Pilot took four high-level metrics, the 2019 edition of
InCiSE will use 13 more granular metrics.

The eGBR uses mystery shopping of eight 'life events' to assess the quality of
digital public services in all 28 EU member countries and six other
neighbouring/partner countries. These life events are designed to capture the
majority of interactions that citizens and businesses have with public services
in European nations. The services assessed by the eGBR include not only
national level services but also those provided by sub-national and local
governments. As InCiSE aims to look at the effectiveness of national-level
civil services we investigated whether there was a way to exclude non-national
services.

While the European Commission publishes the full underlying data for the eGBR,
it is not easy to calculate scores based solely on the assessments of
national-level services. So, an analysis of the data from the 2016 and 2017
reports was undertaken to look at the pattern of service delivery across the
eight life events. The results of this analysis is presented in Table 3.12.C,
and shows that for five of the eight life events more than half of the URLs
assessed by the eGBR are recorded as 'national' level services. However, for
the 'moving house', 'owning and driving a car' and 'studying' life events the
analysis shows that in most countries the URLs being assessed are sub-national/
local services.

```{r}
#| label: tbl-egbr-nat
#| tbl-cap: Proportion of eGBR assessed services identified as 'national'
#|   level services

tbl_egbr_nat |>
  gt::gt() |>
  gt::cols_label(
    life_event = "Life event",
    median_national = "Median proportion of country assessed URLs that are for 'national' services",
    low_national = "Number of countries where less than 50% of assessed URLs are for 'national' services (out of 34)"
  ) |>
  gt::tab_footnote("Table 3.12.C in the original 2019 publication") |>
  strip_gt()

```

For each of the eight life events the mystery shopping exercise looks across
three domains: 'user centric government', 'transparency' and 'key enablers';
six of the eight life events are also assessed for the additional domain of
'cross-border mobility'. As transparency is already covered in InCiSE through
the openness indicator, including the eGBR transparency data could be seen as
duplicating information already measured elsewhere in the InCiSE framework.

Therefore, in the 2019 edition of InCiSE rather than use the high-level
averages for the four domains (as used in the 2017Pilot), the model uses the
'user centric', 'transparency' and 'key enablers' domain scores for the
business start-up, regular business operations, family life, losing and
finding a job, and small claims procedure life events. This approach removes
scores for the three life events (moving house, owning and driving a car,
and studying) where services are typically not delivered by national
governments, and reduces potential overlap with the openness indicator by
removing scores for the 'transparency' domain.

::: {.callout-note .crf title="Cross-referencing note" icon="false"}

This chapter was presented as section 3.12 in the original 2019 publication.

:::
