---
execute:
  echo: false
---

```{r, setup}
#| output: false
source("R/tbl_helpers.R")

tbl_3 <- readr::read_csv("tables/table_3.csv") |>
  dplyr::mutate(
    proxy = dplyr::if_else(proxy, "Yes", "No"),
    label = dplyr::if_else(new, paste0(label, " [new]"), label),
    wt_intheme = formattable::percent(1/wt_intheme, 1),
    wt_theme = formattable::percent(1/wt_theme, 1),
    wt_total = formattable::percent(wt_intheme * wt_theme, 1)
  )

```

# Tax administration {#sec-method-tax}

<!-- This is chapter 3, section 11 in the original PDF -->

The tax administration indicator is defined as: the efficiency and
effectiveness of tax collection (at the central/federal level). Effective tax
systems can be viewed as a critical building block for increased domestic
resource mobilisation which is essential for civil service effectiveness and
good governance. "Successful tax extraction provides resources that enable the
government to operate in other domains", @fukuyama_what_2013 highlights "it is
a necessary function of all states, and one for which considerable data exist".
The role of tax administration as the basis of government operations is made
clear by the @oecd_building_nodate: "Strong tax administrations and sound public
financial management help maximise the domestic resources that are necessary
for government to function, to sustain social safety nets, to maintain
long-term fiscal sustainability, and to free up fiscal space for pursuing
socio-economics objectives". Although priorities and circumstances vary widely
across countries, the drive to elevate the collective standard of tax
administration is of great importance. Holt and Manning highlight the
importance of tax administration in measuring the effectiveness of public
administration and it is one of the key functions highlighted by the 
@world_bank_indicators_2012.

The tax administration indicator is comprised of six metrics and its structure
is unchanged from the 2017 Pilot edition of InCiSE. The data sources for the
indicator are:

* OECD's Tax Administration Comparative Information Series [2015].
* The World Bank's 'Doing Business' Index (WB) [2018].

```{r}
#| label: tbl-comp-tax
#| tbl-cap: Composition of the tax administration indicator
#| column: screen-inset-right
#| classes: no-stripe .table-responsive

tbl_3 |>
  composition_table("TAX") |>
  gt::tab_footnote("Tables 3.11.A & 3.11.B in the original 2019 publication") |>
  strip_gt()

```

## Imputation of missing data {#sec-tax-imputation}

None of the 38 countries selected for the 2019 edition of InCiSE have
completely missing data for the tax administration metrics. As a result the
imputation of missing data for the tax administration metrics is based solely
on the data within the indicator.

## Changes from the 2017 Pilot {#sec-tax-changes}

There are no changes to the structure of the tax administration indicator.

::: {.callout-note .crf title="Cross-referencing note" icon="false"}

This chapter was presented as section 3.11 in the original 2019 publication.

:::
