---
execute:
  echo: false
---

```{r, setup}
#| output: false
source("R/tbl_helpers.R")

tbl_3 <- readr::read_csv("tables/table_3.csv") |>
  dplyr::mutate(
    proxy = dplyr::if_else(proxy, "Yes", "No"),
    label = dplyr::if_else(new, paste0(label, " [new]"), label),
    wt_intheme = formattable::percent(1/wt_intheme, 1),
    wt_theme = formattable::percent(1/wt_theme, 1),
    wt_total = formattable::percent(wt_intheme * wt_theme, 1)
  )

```

# HR management {#sec-method-hrm}

<!-- This is chapter 3, section 10 in the original PDF -->

The HR Management indicator is defined as: the meritocracy of recruitment and
extent to which civil servants are effectively attracted, managed and
developed. "The public sector is very labour intensive – around 70 per cent of
the budgets of most public organisations are spent on staff"
[@boviard_public_2003], so good HR management is key to the successful
functioning of an exemplary civil service. Performance management can help
create incentives for personal development in the civil service.
@fukuyama_what_2013 recognises that recruitment and reward "remain at the
core of any measure of quality of governance. Whether bureaucrats are recruited
and promoted on the basis of merit". Meanwhile, @boviard_public_2003 note that
"if the HR policies are not right, then public organisations will not attract
the human resources they need to perform the functions of government and
deliver the services that government has promised the electorate".

The HR management indicator is comprised of nine metrics, an increase of four
from the 2017 Pilot. The data sources for the indicator are:

* Quality of Government expert survey by the University of Gothenburg
  (QoG) [2015].
* OECD survey on Strategic HumanResources Management (OECD) [2016].

```{r}
#| label: tbl-comp-hrm
#| tbl-cap: Composition of the HR management indicator
#| column: screen-inset-right
#| classes: no-stripe .table-responsive

tbl_3 |>
  composition_table("HRM") |>
  gt::tab_footnote("Tables 3.10.A & 3.10.B in the original 2019 publication") |>
  strip_gt()

```

## Imputation of missing data {#sec-hrm-imputation}

None of the 38 countries selected for the 2019 edition of InCiSE have
completely missing data for the HR management metrics. As a result the
imputation of missing data for the HR management metrics is based solely on
the data within the indicator.

## Changes from the 2017 Pilot {#sec-hrm-changes}

In the 2017 Pilot, InCiSE used five metrics from the Quality of Governance
study. These provided only partial coverage of the topic area, with a
particularly strong focus on meritocratic recruitment. Since the 2017 Pilot,
the OECD published the 2017 edition of their Government at a Glance report,
including a number of measures from their 2016 Survey on Strategic Human
Resource Management. The 2019 edition of InCiSE has incorporated three metrics
from this survey as published in Government at a Glance in order to improve
the coverage of the indicator.

While there continue to be arguments about the use and implementation of
performance appraisal and performance-related pay mechanisms within public
sector organisations, the OECD (2005) suggests that even if there is no direct
performance improvement associated with these measures they can act as a
catalyst for change. Thus, there may be secondary effects from performance
appraisal and performance related pay that improve civil service
effectiveness.

::: {.callout-note .crf title="Cross-referencing note" icon="false"}

This chapter was presented as section 3.10 in the original 2019 publication.

:::
