---
execute:
  echo: false
---

```{r, setup}
#| output: false
source("R/tbl_helpers.R")
tbl_A <- readr::read_csv("tables/table_A.csv")

```

# Composite metrics {#sec-composite-metrics}

Most metrics in InCiSE are variables taken directly from the source datasets.
Some of these metrics are themselves an index or composite score, where this
composite is calculated by the source provider the metric is taken "as is" by
InCiSE. However, some of the source variables identified for inclusion in
InCiSE are binary information (e.g. yes/no questions, or representing
categorical data). 

In the case of inclusiveness the InCiSE model calculates the absolute
difference between the composition of central government employees and the
composition of the general labour market. This Annex provides details on how
the composite metrics calculated by the InCiSE methodology have been produced. 

Including binary variables directly into the InCiSE model presents challenges
in respect of the usability of the model's results. Firstly, it has the
potential for some indicators to become difficult to summarise due to the
large number of metrics they would record – in the most extreme case the
crisis and risk management indicator would be based on 68 metrics. Secondly,
by their nature, binary variables have only two positions, meaning that a
country would either score 0 or 1 with no variation between these two
positions, limiting the ability to distinguish between relative country
performance. To resolve these limitations, the InCiSE model combines binary
variables into composite aggregate metrics. These composite metrics have been
designed within the InCiSE project's methodology, and have not been developed
by the authors/ publishers of the source data. In general, InCiSE maintains
conceptual consistency (e.g. the composite metric aggregates information about
similar) and source consistency (i.e. a composite metric is an aggregation of
variables from the same dataset from the same author/publisher). 

## Integrity {#sec-composite-integrity}

```{r}
#| label: tbl-composite-int
#| tbl-cap: Composite metrics in the integrity indicator

composite_metrics_table(tbl_A, "INT",
                        "Table A.1 in the original PDF publication")
```

See @sec-method-integrity for the full composition of the integrity indicator,
@sec-integrity-changes provides more in-depth discussion about the coding of
post-employment cooling-off periods.

## Inclusiveness  {#sec-composite-inclusiveness}

```{r}
#| label: tbl-composite-inc
#| tbl-cap: Composite metrics in the inclusiveness indicator

composite_metrics_table(tbl_A, "INC",
                        "Table A.2 in the original PDF publication")
```

See @sec-method-inclusiveness for the full composition of the inclusiveness
indicator.

## Fiscal and financial management  {#sec-composite-ffm}

```{r}
#| label: tbl-composite-ffm
#| tbl-cap: Composite metrics in the fiscal and financial management indicator

composite_metrics_table(tbl_A, "FFM",
                        "Table A.3 in the original PDF publication")
```

See @sec-method-fiscal for the full composition of the fiscal and financial
management indicator.

## Tax administration {#sec-composite-tax}

```{r}
#| label: tbl-composite-tax
#| tbl-cap: Composite metrics in the tax administration indicator

composite_metrics_table(tbl_A, "TAX",
                        "Table A.4 in the original PDF publication") 
```

See @sec-method-tax for the full composition of the tax administration
indicator.

## Procurement {#sec-composite-procurement}

```{r}
#| label: tbl-composite-pro
#| tbl-cap: Composite metrics in the procurement indicator

composite_metrics_table(tbl_A, "PRO",
                        "Table A.5 in the original PDF publication")
```

The source data for e-procurement functions indicates whether these functions
are available in national e-procurement systems and in e-procurement systems
for (some) individual entities. Where a country has the functionality in a
national system this is coded as 1 (irrespective of whether exists in the
systems of individual entities), where there is no functionality indicated in
a national system but it is available in some individual entities this is coded
as 0.5.

See @sec-method-procurement for the full composition of the procurement
indicator.

## Crisis and risk management {#sec-composite-crm}

```{r}
#| label: tbl-composite-crm
#| tbl-cap: Composite metrics in the crisis and risk management indicator

composite_metrics_table(tbl_A, "CRM",
                        "Table A.6 in the original PDF publication")
```

See @sec-method-crisis for the full composition of the crisis and risk
management indicator.
