---
execute:
  echo: false
---

```{r, setup}
#| output: false

source("R/tbl_helpers.R")

tbl_sens_country <- read_md_tbl("tables/table_B-1.txt")

tbl_sens_date <- read_md_tbl("tables/table_B-2.txt")

tbl_sens_wght <- read_md_tbl("tables/table_B-3.txt")

tbl_sens_base <- read_md_tbl("tables/table_B-4.txt")

tbl_sens_imp <- read_md_tbl("tables/table_B-5.txt")

```

# Sensitivity analysis: detailed results {#sec-sensitivity-detailed}

This Annex provides detailed results from the sensitivity analysis described
in @sec-sensitivity. Each table includes the index score and rank for each of
the 38 countries included in the 2019 InCiSE Index results for each of the
sensitivity tests carried out alongside the results of the 2019 index results. 

@tbl-sens-country shows the results of the sensitivity tests varying country
coverage (@sec-sens-country):

* Using a data quality assessment threshold of 0.55 to determine country
  inclusion; 
* Using a data quality assessment threshold of 0.6 to determine country
  inclusion; 
* Using a threshold of 75% of the available data to determine country
  inclusion; 
* Using only the countries included in the 2017 Pilot edition of the index. 

@tbl-sens-date shows the results of the sensitivity tests varying the reference
date (@sec-sens-date): 

* Excluding the capabilities indicator; 
* Excluding the capabilities indicator and adjusting the weighting
  accordingly; 
* Using only data with a reference year of 2015 or later; 
* Using only data with a reference year of 2016 or later. 

@tbl-sens-weight shows the results of the sensitivity tests using alternative
weighting (@sec-sens-weight):

* Using a 50:50 split for the equal-share and data-quality based weighting; 
* Using only equal indicator weights(i.e. all indicator weights equal 1/12); 
* Using only indicator weights based on the data quality assessment results; 
* Not applying any within-indicator weights; 
* Calculating the index as a sum of all metrics. 

@tbl-sens-base shows the results of the sensitivity tests adjusting the
base data (@sec-sens-base): 

* Ranking the metrics before imputation; 
* Rescaling the metrics before imputation; 
* Standardising the metrics before imputation. 

@tbl-sens-impute shows the results of the sensitivity tests using alternative
imputation methods (@sec-sens-impute): 

* Using an ‘all-in-one’ approach for imputation of missing data; 
* Using the ‘midas touch’ method for imputation of missing data; 
* Using the ‘random forests’ method for imputation of missing data; 
* Replacing missing data with the mean of observed values.

```{r}
#| label: tbl-sens-country
#| tbl-cap: Sensitivity tests varying country coverage

tbl_sens_country |>
  gt::gt() |>
  gt::cols_label(
    cc_iso3c = "Country",
    incise_2019 = "2019 results",
    sens_55 = "DQA ≥ 0.55",
    sens_60 = "DQA ≥ 0.6",
    sens_75 = "75% of data",
    sens_2017 = "2017 group",
    rank_2019 = "2019 results",
    rank_55 = "DQA ≥ 0.55",
    rank_60 = "DQA ≥ 0.6",
    rank_75 = "75% of data",
    rank_2017 = "2017 group"
  ) |>
  gt::tab_spanner(
    label = "Index score", c(incise_2019, starts_with("sens"))
  ) |>
  gt::tab_spanner(
    label = "Country rank", starts_with("rank")
  ) |>
  gt::sub_missing(missing_text = "", columns = c(-cc_iso3c, -incise_2019)) |>
  gt::sub_missing(missing_text = "---", columns = c(incise_2019)) |>
  gt::cols_align(align = "center", columns = c(-cc_iso3c)) |>
  gt::tab_footnote("Table B.1 in the original PDF publication") |>
  strip_gt()

```

```{r}
#| label: tbl-sens-date
#| tbl-cap: Sensitivity tests varying reference year

tbl_sens_date |>
  gt::gt() |>
  gt::cols_label(
    cc_iso3c = "Country",
    incise_2019 = "2019 results",
    sens_cap1 = "Excl. CAP",
    sens_cap2 = "Excl. CAP & reweight",
    sens_2015 = "2015-2018 data",
    sens_2016 = "2016-2018 data",
    rank_2019 = "2019 results",
    rank_cap1 = "Excl. CAP",
    rank_cap2 = "Excl. CAP & reweight",
    rank_2015 = "2015-2018 data",
    rank_2016 = "2016-2018 data"
  ) |>
  gt::tab_spanner(
    label = "Index score", c(incise_2019, starts_with("sens"))
  ) |>
  gt::tab_spanner(
    label = "Country rank", starts_with("rank")
  ) |>
  gt::sub_missing(missing_text = "", columns = c(-cc_iso3c, -incise_2019)) |>
  gt::sub_missing(missing_text = "---", columns = c(incise_2019)) |>
  gt::cols_align(align = "center", columns = c(-cc_iso3c)) |>
  gt::tab_footnote("Table B.2 in the original PDF publication") |>
  strip_gt()

```

```{r}
#| label: tbl-sens-weight
#| tbl-cap: Sensitivity tests with alternative approaches to weighting

tbl_sens_wght |>
  gt::gt() |>
  gt::cols_label(
    cc_iso3c = "Country",
    incise_2019 = "2019 results",
    sens_5050 = "50:50",
    sens_equal = "Equal weights",
    sens_dqa = "All DQA weights",
    sens_internal = "No within indicator",
    sens_sum = "Sum of metrics",
    rank_2019 = "2019 results",
    rank_5050 = "50:50",
    rank_equal = "Equal weights",
    rank_dqa = "All DQA weights",
    rank_internal = "No within indicator",
    rank_sum = "Sum of metrics"
  ) |>
  gt::tab_spanner(
    label = "Index score", c(incise_2019, starts_with("sens"))
  ) |>
  gt::tab_spanner(
    label = "Country rank", starts_with("rank")
  ) |>
  gt::sub_missing(missing_text = "", columns = c(-cc_iso3c, -incise_2019)) |>
  gt::sub_missing(missing_text = "---", columns = c(incise_2019)) |>
  gt::cols_align(align = "center", columns = c(-cc_iso3c)) |>
  gt::tab_footnote("Table B.3 in the original PDF publication") |>
  strip_gt()

```

```{r}
#| label: tbl-sens-base
#| tbl-cap: Sensitivity tests adjusting the base data

tbl_sens_base |>
  gt::gt() |>
  gt::cols_label(
    cc_iso3c = "Country",
    incise_2019 = "2019 results",
    sens_rank = "Ranked data",
    sens_rescale = "Rescaled data",
    sens_std = "Standardise data",
    rank_2019 = "2019 results",
    rank_rank = "Ranked data",
    rank_rescale = "Rescaled data",
    rank_std = "Standardise data"
  ) |>
  gt::tab_spanner(
    label = "Index score", c(incise_2019, starts_with("sens"))
  ) |>
  gt::tab_spanner(
    label = "Country rank", starts_with("rank")
  ) |>
  gt::sub_missing(missing_text = "", columns = c(-cc_iso3c, -incise_2019)) |>
  gt::sub_missing(missing_text = "---", columns = c(incise_2019)) |>
  gt::cols_align(align = "center", columns = c(-cc_iso3c)) |>
  gt::tab_footnote("Table B.4 in the original PDF publication") |>
  strip_gt()

```


```{r}
#| label: tbl-sens-impute
#| tbl-cap: Sensitivity tests adjusting the base data

tbl_sens_imp |>
  gt::gt() |>
  gt::cols_label(
    cc_iso3c = "Country",
    incise_2019 = "2019 results",
    sens_allin = "All-in-one",
    sens_midas = "Midas touch",
    sens_rf = "Random forests",
    sens_mean = "Mean value",
    rank_2019 = "2019 results",
    rank_allin = "All-in-one",
    rank_midas = "Midas touch",
    rank_rf = "Random forests",
    rank_mean = "Mean value"
  ) |>
  gt::tab_spanner(
    label = "Index score", c(incise_2019, starts_with("sens"))
  ) |>
  gt::tab_spanner(
    label = "Country rank", starts_with("rank")
  ) |>
  gt::sub_missing(missing_text = "", columns = c(-cc_iso3c, -incise_2019)) |>
  gt::sub_missing(missing_text = "---", columns = c(incise_2019)) |>
  gt::cols_align(align = "center", columns = c(-cc_iso3c)) |>
  gt::tab_footnote("Table B.5 in the original PDF publication") |>
  strip_gt()

```
